---
title: "Tourism project"
author: "Lounès AÏT KARROU & Jinane AMAL"
format: pdf
editor: visual
---

```{r}
#| message: false
library(here)
library(dplyr)
library(tidyr)
library(ggplot2)
library(knitr)
library(corrplot)
library(car)
theme_set(theme_bw())
here::i_am("TourismProject.Rproj")
```

# I. Loading the data

```{r}
Arrivals<-read.csv("Datas/arrivals.csv",sep=";")
AvgExpenditures<-read.csv("Datas/avexpinttourists.csv",sep=";")
FoodExpenditures<-read.csv("Datas/foodexp.csv",sep=";")
GDP<-read.csv("Datas/gdppercap.csv",sep=";")
Gini<-read.csv("Datas/gini.csv",sep=";")
Happy<-read.csv("Datas/happinessladder.csv",sep=";")
TerrorDeath<-read.csv("Datas/terrorism-deaths.csv",sep=";")
Forest<-read.csv("Datas/propofprotectedforests.csv",sep=";")
```

# II. Sources and GitHub

You can have access to the source of our data by clicking on the name of the variable :

-   [Average expenditures by tourist](https://ourworldindata.org/grapher/average-expenditures-of-international-tourists-domestically?tab=table)\
-   [Gross Domestic Product per capita](https://ourworldindata.org/economic-growth#all-charts)
-   [Gini Coefficient](https://ourworldindata.org/grapher/economic-inequality-gini-index)
-   [Number of arrivals](https://data.worldbank.org/indicator/ST.INT.ARVL?end=2020&most_recent_year_desc=false&start=2020&view=bar)
-   [Happiness and life satisfaction](https://ourworldindata.org/happiness-and-life-satisfaction)
-   [Food expenditure](https://ourworldindata.org/grapher/food-expenditure-per-person-per-year?tab=table)
-   [GDP per capita](https://ourworldindata.org/grapher/gdp-per-capita-worldbank?tab=table)
-   [Terrorism death](https://ourworldindata.org/grapher/terrorism-deaths)

Click [here](https://github.com/jinane1amal/TourismProject.git) to access to our GitHub project.

# III. Description of our sources

To get our data, we decide to use two different data banks.

First, we have used is the research publication called "Our World in Data". Founded by the economist Max Roser in 2011, "Our World in Data" is working in collaboration with thousands of researchers all around the world to try to answer and face the hardest problem our world is facing: poverty, diseases, hunger, climate change, war etc.\
"Our World in Data" uses interactive charts and maps to illustrate the work of the researchers. In this website, we found the data for the following topics :

-   The food expenditures per person from 2017 to 2021
-   The self-reported life satisfaction from 2011 to 2022.
-   The income inequalities measured by the Gini coefficient from 1967 to 2021
-   The share of forest area within protected areas from 2000 to 2020
-   The international tourist expenditures within the country they visit from 1995 to 2021
-   The terrorism deaths from 1970 to 2021
-   The GDP per capita from 1990 to 2021

All this data and their variables are going to be explained in the next part. Note that we are not going to keep those periods, we will deal with this issue later, during the data cleaning part.

We also went to the Data world bank to find our principal data set : the number of arrivals. The World Bank Group, established in 1944 along the International Monetary Fund at the Bretton Woods Conference, is one of the world's largest sources of funding and knowledge for developing countries. Its five institutions share a commitment to reducing poverty, increasing shared prosperity, and promoting sustainable development. This group is dividing in 5 institutions:

-   The international bank for reconstruction\
-   The international development association\
-   The international finance corporation\
-   The multilateral investment guarantee agency\
-   The International Centre for Settlement of Investment Disputes.

Even if their main mission is, as they said themselves, to provide a wide array of financial products and technical assistance but also to help countries share, they also produce data that can be find in their site, where there is a whole page dedicated to a whole free collection of data.

# IV. Description of our data

## A) Number of arrivals: 
#### Tourist arrivals, the primary dependent variable, stand as the pivotal metric impacted by chosen independent variables, shaping a country's overall attractiveness to tourism. Understanding and optimizing these influential factors can significantly influence the influx of visitors.

### Data set A cleaning task 1 : Focus (2019 VS 2020)

```{r}
Arrivals19vs20 <- Arrivals |>
  select(1:2, 64:65)
```

### Data set A cleaning task 2 : alphabetical order

```{r}
Arrivals19vs20 <- Arrivals19vs20 |>
  arrange(Country.Name)
```

### Data set A cleaning task 3 : Renaming all 4 columns

```{r}
Arrivals19vs20 <- Arrivals19vs20|>
  rename(Country=Country.Name, Code= Country.Code, "2019" = X2019 , "2020" = X2020)
```

### Cleaned Data set A Summary

# Get number of rows and columns

```{r}
nbrows <- nrow(Arrivals19vs20 %>% distinct(Country))
nbcol <- ncol(Arrivals19vs20)
```

The Cleaned Data set A Summary contains `r nbrows` number of columns and `r nbcol` number of rows


<<<<<<< HEAD

=======


### Cleaned Data set A Summary to be shown in html rendering:
```{r}
print(summary(Arrivals19vs20))|>
knitr::kable()
```
>>>>>>> 691925d3e6d4f911657d46601bd0598b97b931e0

# Get number of rows and columns

```{r}
nbrows <- nrow(Arrivals19vs20 %>% distinct(Country))
nbcol <- ncol(Arrivals19vs20)
```

The Cleaned Data set A Summary contains `r nbrows` number of columns and `r nbcol` number of rows.


## B) Average Expenditures:
#### Average expenditures, as the second dependent variable, are intricately influenced by factors like cultural offerings and safety measures, shaping a country's overall appeal to tourism. These variables contribute to the financial decisions of tourists, impacting the level of spending and economic contributions within the destination.

### Data set B cleaning task 1 : Focus (2019 VS 2020)

```{r}

AvgExpenditures19vs20 <- AvgExpenditures|>
  filter(Year %in% c(2019, 2020))
```

### Data set B cleaning task 2 : Pivoting

```{r}
AvgExpenditures19vs20v1 <- AvgExpenditures19vs20|>
   pivot_wider(names_from= Year, values_from=Inbound_Tourism_Expenditure_adjusted)
```

### Data set B cleaning task 3 : Renaming the first column

```{r}
AvgExpenditures19vs20v1 <- AvgExpenditures19vs20v1|>
  rename(Country=Entity)
```

### Data set B cleaning task 4 : Mutating the last 2 columns to be recognised as numerical values
```{r}
AvgExpenditures19vs20v1 <- AvgExpenditures19vs20v1 |>
  mutate_at(vars("2019", "2020"), as.numeric)
```

### Cleaned Data set B Summary

```{r}
print(names(AvgExpenditures19vs20v1))
print(dim(AvgExpenditures19vs20v1))
print(summary(AvgExpenditures19vs20v1))
```

### Cleaned Data set B Summary to be shown in html rendering :

```{r}
print(summary(AvgExpenditures19vs20v1))|>
knitr::kable()
```

# Get number of rows and columns

```{r}
nbrows <- nrow(AvgExpenditures19vs20v1 %>% distinct(Country))
nbcol <- ncol(AvgExpenditures19vs20v1)
```

The Cleaned Data set B Summary contains `r nbrows` number of columns and `r nbcol` number of rows.

## C) Food Expenditures:

#### Food expenditures, as an independent variable, directly impact a country's tourism attractiveness by influencing the accessibility and affordability of diverse culinary experiences, shaping the overall appeal for travelers. 

### Data set C cleaning task 1 : Focus (2019 VS 2020)

```{r}
FoodExpenditures19vs20<- FoodExpenditures |>
  filter(Year %in% c(2019, 2020))
```

### Data set C cleaning task 2: Pivoting

```{r}
FoodExpenditures19vs20v1<- FoodExpenditures19vs20 |>
    pivot_wider(names_from= Year, values_from=Total.food.expenditure)
  
```

### Data set C cleaning task 3 : Renaming the first column

```{r}
FoodExpenditures19vs20v1 <- FoodExpenditures19vs20v1|>
  rename(Country=Entity)
```

### Cleaned Data set C Summary

```{r}
print(names(FoodExpenditures19vs20v1))
print(dim(FoodExpenditures19vs20v1))
print(summary(FoodExpenditures19vs20v1))
```

### Cleaned Data set C Summary to be shown in html rendering :

```{r}
print(summary(FoodExpenditures19vs20v1))|>
knitr::kable()
```

# Get number of rows and columns

```{r}
nbrows <- nrow(FoodExpenditures19vs20v1 %>% distinct(Country))
nbcol <- ncol(FoodExpenditures19vs20v1)
```

The Cleaned Data set C Summary contains `r nbrows` number of columns and `r nbcol` number of rows.

## D) Forest:

#### The extent of protected forest surface in a country serves as an independent variable influencing its tourism attractiveness, signifying environmental conservation and offering unique natural attractions. 

### Data set D cleaning task 1 : change 0s into NA

```{r}
Forest <- Forest|>
 mutate_all(~ifelse(. == 0, NA, .))
```

### Data set D cleaning task 2 : Get rid of NA lines

```{r}
Forest <- Forest|>
  filter(!is.na(Code))
```

### Data set D cleaning task 3 : Focus (2019 VS 2020)

```{r}
Forest19vs20 <- Forest |>
  filter(Year %in% c(2019, 2020))
```

### Data set D cleaning task 4 : pivoting

```{r}
Forest19vs20v1 <- Forest19vs20 |>
    pivot_wider(names_from= Year, values_from= Proportionofprotectedforests)
```

### Data set D cleaning task 5 : Renaming the first column

```{r}
Forest19vs20v1 <- Forest19vs20v1|>
  rename(Country=Entity)
```

### Cleaned Data set D Summary

```{r}
print(names(Forest19vs20v1))
print(dim(Forest19vs20v1))
print(summary(Forest19vs20v1))
```

### Cleaned Data set C Summary to be shown in html rendering

```{r}
print(summary(Forest19vs20v1))|>
knitr::kable()
```

# Get number of rows and columns

```{r}
nbrows <- nrow(Forest19vs20v1 %>% distinct(Country))
nbcol <- ncol(Forest19vs20v1)
```

The Cleaned Data set D Summary contains `r nbrows` number of columns and `r nbcol` number of rows.

## E) Gross Domestic Product per capita :

#### High GDP signifies Economic prosperity which often translates into improved amenities, accessibility, and diverse attractions, making the destination more appealing to tourists.

### Data set E cleaning task 1 : Focus (2019 VS 2020)

```{r}
GDP19vs20 <- GDP |>
  select(1:2, 64:65)
```

### Data set E cleaning task 2 : Renaming all 4 columns

```{r}
GDP19vs20 <- GDP19vs20|>
  rename(Country= Country.Name, Code= Country.Code, "2019" = X2019 , "2020" = X2020)
```

### Cleaned Data set E Summary

```{r}
print(names(GDP19vs20))
print(dim(GDP19vs20))
print(summary(GDP19vs20))
```

### Cleaned Data set E Summary to be shown in html rendering :
```{r}
print(summary(GDP19vs20))|>
knitr::kable()
```

# Get number of rows and columns

```{r}
nbrows <- nrow(GDP19vs20 %>% distinct(Country))
nbcol <- ncol(GDP19vs20)
```

The Cleaned Data set E Summary contains `r nbrows` number of columns and `r nbcol` number of rows.

## F) GINI Index :

#### The Gini Index measures income inequality within a country, with higher values indicating greater inequality. High Gini Index scores may negatively impact a country's attractiveness to tourism, as economic disparities can affect overall stability and inclusivity, influencing visitors' perceptions and experiences.

### Data set F cleaning task 1 : Focus (2019 VS 2020)

```{r}
Gini19vs20 <- Gini |>
  filter(Year %in% c(2019, 2020))
```

### Data set F cleaning task 2 : Getting rid of the additional lines for urban or rural region for which we already have an average gini coefficient

```{r}
Gini19vs20 <- Gini19vs20|>
  filter(!grepl(" - (rural|urban)$", Entity))
```

### Data set F cleaning task 3 : pivoting

```{r}
Gini19vs20v1 <- Gini19vs20 |>
    pivot_wider(names_from= Year, values_from= Gini.coefficient)
```

### Data set C cleaning task 4 : Renaming the first column

```{r}
Gini19vs20v1 <- Gini19vs20v1|>
  rename(Country=Entity)
```



### Cleaned Data set F Summary

```{r}
print(names(Gini19vs20v1))
print(dim(Gini19vs20v1))
print(summary(Gini19vs20v1))
```

### Cleaned Data set F Summary to be shown in html rendering
```{r}
print(summary(Gini19vs20v1))|>
knitr::kable()
```

# Get number of rows and columns

```{r}
nbrows <- nrow(Gini19vs20v1 %>% distinct(Country))
nbcol <- ncol(Gini19vs20v1)
```

The Cleaned Data set F Summary contains `r nbrows` number of columns and `r nbcol` number of rows.

## G) Happiness Ladder :

#### The Happiness Ladder, a measure of a country's overall well-being and life satisfaction, serves as a pivotal independent variable influencing its attractiveness to tourism. Higher rankings on the Happiness Ladder often correlate with a positive perception, encouraging tourists to seek enriching and joyful experiences in those destinations.

### Data set G cleaning task 1 : Focus (2019 VS 2020)

```{r}
Happy19vs20 <- Happy |>
  filter(Year %in% c(2019, 2020))
```

### Data set G cleaning task 2 : pivoting

```{r}
Happy19vs20v1 <- Happy19vs20 |>
    pivot_wider(names_from= Year, values_from= Cantril.ladder.score)
```

### Data set G cleaning task 3 : Renaming the first column

```{r}
Happy19vs20v1 <- Happy19vs20v1|>
  rename(Country=Entity)
```

### Data set G cleaning task 4 : Switching the order of the last 2 columns representing our focused years of study

```{r}
Happy19vs20v1 <- Happy19vs20v1|>
  select(-"2019", -"2020", "2019", "2020")
```

### Cleaned Data set G Summary

```{r}
print(names(Happy19vs20v1))
print(dim(Happy19vs20v1))
print(summary(Happy19vs20v1))
```

### Cleaned Data set G Summary to be shown in html rendering :
```{r}
print(summary(Happy19vs20v1))|>
knitr::kable()
```

# Get number of rows and columns

```{r}
nbrows <- nrow(Happy19vs20v1 %>% distinct(Country))
nbcol <- ncol(Happy19vs20v1)
```

The Cleaned Data set G Summary contains `r nbrows` number of columns and `r nbcol` number of rows.

## H) Terrorism Attacks

#### Terrorist attacks act as an independent variable negatively impacting a country's attractiveness to tourism, creating safety concerns and deterring potential visitors. The frequency and severity of such incidents significantly influence the perceived security of a destination, shaping tourists' decisions and preferences.

### Data set H cleaning task 1 : Focus (2019 VS 2020)

```{r}
TerrorDeath19vs20 <- TerrorDeath |>
  filter(Year %in% c(2019, 2020))
```
### Data set H cleaning task 2 : Get rid 0's into NA

```{r}
TerrorDeath19vs20 <- TerrorDeath19vs20|>
 mutate_all(~ifelse(. == 0, NA, .))
```

### Data set H cleaning task 3 : Get rid of NA lines

```{r}
TerrorDeath19vs20 <- TerrorDeath19vs20|>
  filter(!is.na(Code))
```

### Data set H cleaning task 4 : Since previous command changes the values into NA's we should now revert the NA'S of the last column to 0 (mening no terrorist attack)

```{r}
TerrorDeath19vs20[is.na(TerrorDeath19vs20[, ncol(TerrorDeath19vs20)]), ncol(TerrorDeath19vs20)] <- 0

```
### Data set H cleaning task 5 : Renaming the first column

```{r}
TerrorDeath19vs20 <- TerrorDeath19vs20|>
  rename(Country=Entity)
```

### Data set D cleaning task 6 : pivoting

```{r}
TerrorDeath19vs20v1 <- TerrorDeath19vs20 |>
    pivot_wider(names_from= Year, values_from= Terrorism.deaths)
```

### Cleaned Data set H Summary

```{r}
print(names(TerrorDeath19vs20v1))
print(dim(TerrorDeath19vs20v1))
print(summary(TerrorDeath19vs20v1))
```

### Cleaned Data set H Summary to be shown in html rendering:

```{r}
print(summary(TerrorDeath19vs20v1))|>
knitr::kable()
```


# Get number of rows and columns

```{r}
nbrows <- nrow(TerrorDeath19vs20v1 %>% distinct(Country))
nbcol <- ncol(TerrorDeath19vs20v1)
```

The Cleaned Data set H Summary contains `r nbrows` number of columns and `r nbcol` number of rows.

# V. Description of our Research Question :

## "What makes a country more attractive to tourists ?"

Travel holds profound importance in our lives, extending far beyond the mere act of moving from one place to another.
It serves as a gateway to diverse cultures, broadening our perspectives and fostering a deeper understanding of the world.
The importance of travel lies not only in the personal enrichment it offers but also in the role it plays in showcasing a country's distinctive charm. 
Every nation becomes a storyteller, enticing visitors with its rich history, cultural treasures, and breathtaking landscapes. 
Tourism becomes a bridge between cultures, a means to celebrate diversity and foster global understanding. As we explore different corners of the world, we contribute to a shared narrative of interconnectedness, where each country's unique appeal adds vibrancy to the collective tapestry of global tourism.
Therefore, understanding the factors that make a destination appealing becomes a fascinating research endeavor. 
As we embark on this research trail, the pivotal question arises: "What makes a country more attractive to tourists?" 
This question will focus on a comparison study between 2 years 2019 & 2020 :
2019 which will represent the initial tourism trends before the pandemic and 2020 will show us how the covid pandemic impacted these tourism trends through the evolution of the chosen variables 
This query seeks to unravel the distinct elements that shape a nation's allure, delving into cultural, environmental, infrastructural and economy oriented facets that draw visitors. By exploring this question, we aim to not only enrich our comprehension of travel dynamics but also contribute valuable insights to the ongoing dialogue on global tourism trends.
In evaluating a country's tourism success, we are focusing on the number of tourist arrivals. The number of arrivals serves as a primary indicator, reflecting the appeal and popularity of a destination, while average expenditure provides insights into the economic impact of tourism. To understand the influencing factors, we consider various variables. Gross Domestic Product (GDP) reflects the economic strength of a nation, potentially correlating with tourism appeal. Gini coefficient measures income inequality, influencing the distribution of tourist spending. The Happiness Ladder index gauges the overall well-being of a country's population, potentially affecting its attractiveness to visitors. The proportion of protected forests contribute to environmental considerations, influencing sustainable tourism. We also took the food expenditures as another indicator of the affordability experiencing a country's culinary traditions. Lastly, we chose as another variable the number of terrorist attacks per country reflecting the potential danger tourists will face if they visit a country .

# VI. Graphical representation of the main variable

To have a proper representation of our main target variable, we will first transform our data into a long data, to have a column for the two different years. 

```{r}
datalong<-gather(Arrivals19vs20,key="Years",value="Values",-Country, -Code)
```

Now we can, using the ggplot2 library, have the graphical representation :

```{r}
ggplot(datalong, aes(x = Country, y = Values)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~Years, ncol=1) +
  labs(title = "Numbers of arrivals in each country in 2019 and 2020",
       x = "Countries",
       y = "Number of arrivals") +
  theme(axis.text.x = element_text(size = 2, angle = 90))
```
# V. Merged Data set:

Before providing the correlation matrix and the linear regression, we merge our data set using the following code :
We decided to merge our tables using the inner_joint function, joining by the country and the code so we can have the same countries for all the tables.  
Noticed that, due to the numerous number of N.a on the Gini table, we decided to exclude this variable in our study. 

```{r}
TabA<-inner_join(Arrivals19vs20,AvgExpenditures19vs20v1,by=c('Code','Country'),suffix=c('_arrivals','_avg'))
TabB<-inner_join(FoodExpenditures19vs20v1,Forest19vs20v1,by=c('Code','Country'),suffix=c('_food','_forest'))
TabC<-inner_join(GDP19vs20,Happy19vs20v1,by=c('Code','Country'),suffix=c('gdp','_happy') )
TabD<-inner_join(TabA,TabB,by=c('Code','Country'))
Tab <- inner_join(TabD,TabC,by=c('Code','Country'))
print(Tab)|>knitr::kable()
```

# VI. Correlation Matrix:

In this section, we want to quantify the strength of linear relationships between the variables we kept for our following regression through correlation matrices for the two comparison years 2019 vs 2020 .

$$ Focus\ Year\ : 2019 $$
```{r}
corr = cor(subset(Tab, select = c(`2019_arrivals`,`2019_avg`,`2019_food`, `2019_forest`,`2019_happy`,`2019gdp`)))
corrplot(corr, type = "upper", method = "color" , tl.col = "black") 
```
We notice two important things for year 2019:
-First: 3 of the explanatory variables are positively correlated to each other: food, happiness, and the gdp indicators.
-Second: The average expenditure indicator is the only indicator which we can't determine its correlation to other variables  

$$ Focus\ Year\ : 2020 $$
```{r}
corr = cor(subset(Tab, select = c(`2020_arrivals`,`2020_avg`,`2020_food`, `2020_forest`,`2020_happy`,`2020gdp`)))
corrplot(corr, type = "upper", method = "color" , tl.col = "black") 
```
We notice that for year 2020: The obtained correlation matrix slightly resembles the 2019 correlation matrix as much as the 3 positively correlated explanatory variables (food, happiness, and the gdp indicators) are concerned . We also have that 2020_arrivas is this time the only indicator which we can't determine its correlation to other variables .

# VII. Linear regression: 

In this section, we want to study the impact of all the variables on our main variable by using a linear regression. To do so, we will first focus on the impact in 2019 and after that in 2020.   

We want to estimate the following model : 

$$Arrivals=\beta_0+\beta_1AverageExp+\beta_2Food+\beta_3Forest+\beta_4Happy+\beta_5GDP+\varepsilon$$
With $\varepsilon$ the error vector.
```{r}
reg1 <- lm (Tab$'2019_arrivals'~ Tab$'2019_avg'+ Tab$'2019_food' + Tab$'2019_forest' + Tab$'2019_happy' + Tab$'2019gdp' )
summary(reg1)
```


We notice that only a single explanatory variable is significant : `2019_avg`.   
In fact, looking at the value of the t-stat, we have $t_{\beta_1}=4.748$ and since $t^{-1}_{27}(1-\frac{0.05}{2})=2.052$, we get $t_{\beta_1}>t^{-1}_{27}$.    
For all the others explenatory variable, we have the opposite, meaning that they are not significant.    

We do the same but now for the second year of our study :

```{r}
reg2 <- lm (Tab$'2020_arrivals'~ Tab$'2020_avg'+ Tab$'2020_food' + Tab$'2020_forest' + Tab$'2020_happy' + Tab$'2020gdp' )
summary(reg2)
```

Once again, the only significant variable is `2020_avg`.  
    

However, one should pay attention to the value of our adjusted $R^2$. In fact, in both cases, $R^2$ is not high enough (respectively $0.382$ and $0.283$). Thus, maybe this linear regression with thoses explanatory variable is not the best, maybe the unsignificant variable are downgrading the quality of our model, suggesting that those variables may not explain the number of arrivals in a country.  

# VIII. Durbin Watson Test: 
Let's keep our initial model. Indeed, we wish to assess the extent to which this model violates the fundamental assumptions of simple regression.    
To do this, we will carry out the Durbin-Watson test, a test allowing us to highlight a potential autocorrelation of the errors, in other words the errors are correlated. Mathematically, the Durbin-Watson test seeks to verify the significance of the coefficient $\rho$ in the formula:
$$\varepsilon_i=\rho\varepsilon_j+u_i$$
To do so, we will use the `durbinWatsonTest` available on r :

```{r}
durbinWatsonTest (reg1)
durbinWatsonTest (reg2)
```

We observe that, for both regression, the p-value is higher than $0.05$, we won't reject the null hypothesis. In fact, this result could have been more thant predictable since our regression is not temporal and it depends on different countries, so their results and data are not correlated to each other.  

# IX.Plots: 

# IX. Final Scatter plots: 

For the final part of the project, we will focus on the relation between the arrivals and the only significant explanatory variable we found on part VII : the average expenditures.    
To do so, we are going to compare how it would have been if the two variables were perfectly correlated and what is happening in reality.

```{r}

scatterplot(Tab$'2019_arrivals' ~ Tab$'2019_avg', data = Tab, main = "2019 Scatterplot with its Legend", 
            xlab = "2019_avg", ylab = "2019_arrivals")
legend("topright", legend = c("2019_arrivals"), col = c("blue"), pch = 1)


```
 On this graph, the blue line represent the perfect correlation between arrivals and the average expenditures.\\
The blue surface, for its part, represent the average dispertion of our results in real life, from our data, in 2019.    
To observe this dispertion, we also provide below a pair of graph that represent those variable individually.

```{r}
pairs(Tab[, c('2019_avg', '2019_arrivals')], col = "blue", pch = 16)
```
We do the same graphs in 2020.

```{r}

scatterplot(Tab$'2020_arrivals' ~ Tab$'2020_avg', data = Tab, main = "2020 Scatterplot with its Legend", 
            xlab = "2020_avg", ylab = "2020_arrivals")
legend("topright", legend = c("2020_arrivals"), col = c("blue"), pch = 1)

```


```{r}
pairs(Tab[, c('2020_avg', '2020_arrivals')], col = "blue", pch = 16)
```

We can observe that, in both year, there is a correlation between those two variables. They are following the same pattern of growth as we can observe in all of those grpahs, even though at some point the difference between those two is not negligible.    
Those observations are coherent with the obtained results from the two linear regression where the coefficient was positive, translating a positive realtion between the variables.

# X. Conclusion : 

These quantitative analysis has helped us understand what is the most important factor in a country’s tourism attraction .

Our regression results followed by graphical representations proves that the most influential variable throughout both years 2019 and 2020 (covid year) is the average expenditures which is not surprising : Indeed a higher average expenditure in a country is synonymous to  higher quality of services, luxurious experiences, cultural or business events . It can also be a sign of safety.

We can also say that this high rate of tourists arrivals in these countries is achieved via effective marketing and branding which is due to their high money allocated to research and business marketing .

In conclusion average expenditure is key to the success of the country’s tourism objective and this won’t change in the near future .




